Designing and modeling a browser-based distributed evolutionary computation systems

### 2015-04-10 GECCO/modeling-volunteer-computing-gecco.tex
un par de comentarios para tener en cuenta para futuras versiones

At the time of this writing, 23 runs were done in OpenShift and one in
Heroku. The Openshift URL was mentioned more frequently than the other
so that accounts for the popularity, not any particular problem with
the algorithm in one or the other. That is why the data that we have
obtained and used below, and which is, as usual, available with a free
license, is mainly processed from the log files stored in Loggly and
in OpenShift. These 23 experiments took each one a number of hours, so
that in many cases the nodes were not accessing at the same time, but
sequentially, to the server. This means that the island model is, in
fact, behaving partly as a pool-based evolutionary algorithm
\cite{sofea:evopar2012} with some results, the best from each
generation, available to future runs. This is clearly noticed when
visualizing the algorithm: its behavior changes when it gets its first
chromosome from the pool, in many cases improving a lot.

@@

Another interesting result is that we have been able to obtain many
more different users. At the time of this writing we obtained 75
different IPs contributing CPU time to the experiment, giving an
average of around 4 per experiment. However, there is a big variation
in the number of CPUs. There is also a much bigger range in the
performance of these clients. In order to measure that we have
computed the time between two requests from the same IP and plotted it
as an histogram in Figure \ref{fig:intervals}. In that histogram we
can see that there is an almost uniform distribution of intervals,
from the smallest taking a few milliseconds to the biggest with almost
1 second; the setup of the experiment allows it to be accessible from
a very wide range of different IPs. Even within a single IP the
variation can be relatively high, which is shown in a boxplot in
Figure \ref{fig:intervalIP}, sorted by median time. The time between
requests to the server, that is, the time to process 100 generations
of 128 individuals of an evolutionary algorithm to optimize the Trap
function has also very wide range, but even within the same IP,
inter-quartile differences of several hundred milliseconds are not
uncommon. Median for all IPs is 485 milliseconds and average is quite
close, at 496.8 ms.

>>>>

At the time of this writing, 23 runs were done in OpenShift and one in  
% para trabajos futuros, estas cifras de cuántas ejecuciones se han completado 
% quizás habría que presentarlas de forma diferente. Quizás indicando el tiempo
% total de "puesta online" del sistema, cómo se publicitó para atraer gente,
% y entonces ahí contar las estadísticas de cuánta gente partició, cuántas
% ejecuciones se terminaron, etc.  [Pedro]
Heroku. The Openshift URL was mentioned more frequently than the other
so that accounts for the popularity, not any particular problem with
the algorithm in one or the other. That is why the data that we have
obtained and used below, and which is, as usual, available with a free
license, is mainly processed from the log files stored in Loggly and
in OpenShift. These 23 experiments took each one a number of hours, so
that in many cases the nodes were not accessing at the same time, but
sequentially, to the server. This means that the island model is, in
fact, behaving partly as a pool-based evolutionary algorithm
\cite{sofea:evopar2012} with some results, the best from each
generation, available to future runs. This is clearly noticed when
visualizing the algorithm: its behavior changes when it gets its first
chromosome from the pool, in many cases improving a lot.

@@

Another interesting result is that we have been able to obtain many
more different users. At the time of this writing we obtained 75
different IPs contributing CPU time to the experiment, giving an
% ¿se podría hacer en el futuro algún tipo de estudio acerca de la procedencia?
% No estoy seguro de que esa relevante, pero bueno...   [Pedro]
average of around 4 per experiment. However, there is a big variation
in the number of CPUs. There is also a much bigger range in the
performance of these clients. In order to measure that we have
computed the time between two requests from the same IP and plotted it
as an histogram in Figure \ref{fig:intervals}. In that histogram we
can see that there is an almost uniform distribution of intervals,
from the smallest taking a few milliseconds to the biggest with almost
1 second; the setup of the experiment allows it to be accessible from
a very wide range of different IPs. Even within a single IP the
variation can be relatively high, which is shown in a boxplot in
Figure \ref{fig:intervalIP}, sorted by median time. The time between
requests to the server, that is, the time to process 100 generations
of 128 individuals of an evolutionary algorithm to optimize the Trap
function has also very wide range, but even within the same IP,
inter-quartile differences of several hundred milliseconds are not
uncommon. Median for all IPs is 485 milliseconds and average is quite
close, at 496.8 ms.
